### 2015-06-10 auspice_prev/eval-part2.tex
Initial import of thesis starting from proposal document
Includes all files: tex, pdf, etc.

\begin{figure*}[ht]
\vspace{0.05in}
\begin{minipage}[b]{0.48\linewidth}
\centering
\includegraphics[scale=0.55]{graph/newgraphs/managed-lookup.pdf}
\figvsp
\caption{Lookup latency:  \auspice\ with 5 replicas is comparable to UltraDNS (16 replicas); \auspice\ with 15 replicas has 60\% lower latency than UltraDNS.}
\label{fig:managed-lookup}
\end{minipage}
\hspace{0.2in}
\begin{minipage}[b]{0.48\linewidth}
\centering
\includegraphics[scale=0.55]{graph/newgraphs/managed-update.pdf}
\figvsp
\caption{Update propagation delay: \auspice\ with 5 replicas is  1.0 to 24.7 secs lower than three top-tier managed DNS service providers. }
\label{fig:manageddnsupdate}
\end{minipage}
%\hspace{0.3cm}
%\begin{minipage}[b]{0.3\linewidth}
%\centering
%\includegraphics[width=2in,height=1.5in]{graph/medianlatencyVSlocality.pdf}
%\figvsp
%\caption{[Simulator] Workload sensitivity: \auspice\ lowers latency by 2--5$\times$  over \staticthree\ at all geo-locality levels.}
%\label{fig:varylocality}
%\end{minipage}
\vspace{-0.25in}
\end{figure*}

\vsp
\subsection{\auspice\ vs. managed DNS providers}
\label{sec:managed}
%In DNS terminology, an \auspice\ name server provides the functionality of an authoritative name server -- it keeps the most up to date  name-to-address mapping of a host.

Can demand-aware replication benefit commercial managed DNS providers that largely rely on statically replicating today's (hardly mobile) domain names? To investigate this, we compare \auspice\ against three top-tier providers, UltraDNS, DynDNS, and DNSMadeEasy %\cite{ultradns, dyndns, dnsmadeeasy}, 
that offer geo-replicated authoritative DNS services widely used by enterprises (e.g., Dyn provides DNS service for Twitter).

%Having analyzed a synthetic workload dominated by mobile device names, we next evaluate how \auspice\ compares to commercial managed DNS providers in serving their customers' (mostly static) domain names.  These providers such as UltraDNS, DynDNS, and DNSMadeEasy \cite{ultradns, dyndns, dnsmadeeasy} offer a geo-replicated authoritative DNS service and are widely used by enterprises today (e.g., DynDNS provides DNS service for Twitter).

@@

\subsubsection{Lookup latency}

We compare \auspice\ to UltraDNS for a workload of lookups for  domain names serviced by the provider. We identify 316 domain names among the top 10K Alexa websites serviced by this provider, and determine
the geo-distribution of lookups for each name from their data \cite{alexa}.
For each name, we measure the latency for 1000 lookups from across 100 PlanetLab nodes. 
We ensure that lookups are served from the name servers maintained by the provider by requesting the address for a new random sub-domain name each time, e.g, \verb+xqf4p.google.com+ instead of \verb+google.com+, that is unlikely to exist in a cache and requires an authoritative lookup.
\auspice\ name servers are deployed across a total of 80 PlanetLab locations while UltraDNS has 16 known server locations \cite{dnscompare}.  
We evaluate \auspice\ for three configurations  with 5, 10, and 15 replicas of a name respectively.

%For an even comparison between \auspice\ and the provider, we limit the maximum number of replicas/name for \auspice\ to 5, which is less than one-third the number of locations of the provider \cite{dnscompare}.  
%The geo-distribution of lookups for each domain name is determined based on the Alexa dataset \cite{alexa}.

@@

%\begin{figure}[t]
%\centering
%\includegraphics[scale=0.6]{graph/camera-ready/managed-lookup.pdf}
%\vspace{-0.2in}
%\caption{\auspice\ gives better cost-performance tradeoffs than UltraDNS. \auspice\ with 5 replicas has comparable latency to UltraDNS (16 replicas); \auspice\ with 15 replicas has 60\% lower lookup latencies than UltraDNS. Box plot shows 5, 25, 50, 75, and 95 percentiles.}
%\label{fig:managed-lookup}
%\end{figure}

\blue{
Figure \ref{fig:managed-lookup} shows the lookup latencies of names for \auspice\ and for UltraDNS.
UltraDNS incurs a median latency of 45 ms with 16 replicas,  while \auspice\ incurs  41 ms, 22 ms, and 18 ms  respectively with 5, 10, and 15 replicas. 
With 5 replicas, \auspice's performance is comparable to UltraDNS with one-third  the replication cost. 
With 15 replicas, \auspice\ incurs 60\% lower latency for a comparable cost. The comparison against the other two, Dyn and DNSMadeEasy, is qualitatively similar \cite{techreport}.
Thus, \auspice's demand-aware replication achieves a better cost--performance tradeoff compared to static replication.
}

\subsubsection{Update propagation delay} 
To measure update propagation delays, we purchase DNS service from three providers for separate domain names.  All providers replicate a name at 5 locations across US and Europe for the services we purchased. We issue address updates for the domain name serviced by that provider and then immediately start lookups to the authoritative name servers for our domain name.
These authoritative name servers can be queried only via an anycast IP address, i.e., servers at different locations advertise the same externally visible IP address. Therefore, to maximize the number of provider locations queried, we send queries from 50 random PlanetLab nodes. From each location, we periodically send queries until all authoritative name server replicas return the updated address.  The update propagation latency at a node is the time between when the node starts sending lookup to when it receives the updated address. The latency of an update is the the maximum update latency measured at any of the nodes. We measure latency of 100 updates for each provider.
 %is time difference between when we update an address and when the node gets the updated address.

To measure update latencies for \auspice, we replicate 1000 names at a fixed number of PlanetLab nodes across US and Europe. The number of nodes is chosen to be 5, 10, and 20 across three experiments. A client sends an update to the nearest node and waits for update confirmation messages from all replicas. The latency of an update is the time difference between when the client sent an update and when it received the update confirmation message from all replicas (an upper bound on the update propagation delay).  We show the distribution of measured update latencies for \auspice\ and for three managed DNS providers in Figure \ref{fig:manageddnsupdate}.

\auspice\ incurs lower update propagation latencies than all three providers for an equal or greater number of replica locations for names. We were unable to ascertain from UltraDNS why their update latencies are an order of magnitude higher than network propagation delays, but this finding is consistent with a recent study \cite{dnscompare} that has shown latencies of up to tens of seconds for these providers. Indeed, some providers even distinguish themselves by advertising shorter update propagation delays than competitors \cite{dnscompare}.

\subsection{Sensitivity analyses and other results.} 
\label{sec:other} 
We have conducted a comprehensive evaluation of the sensitivity of \auspice's performance-cost trade-offs to workload and system parameters across scales varying by several orders of magnitude. These include workload parameters such as geo-locality, read-to-write rate ratio, ratio of device-to-service names, etc. and system parameters such as the fault-tolerance threshold, capacity utilization, perturbation knob, the tunable overhead of replica reconfiguration, etc. using a combination of simulation and system experiments. These results do not qualitatively change the above findings, and are deferred to the technical report \cite{techreport}.

%To assess the sensitivity of \auspice's benefits to a broad range of system and workload parameters and scales, we develop a custom simulator that simulates round-trip delays, loss, and server load-vs-response time behavior, and have verified \cite{techreport} that the median latencies for all simulated schemes are within 8\% of those in $\S$\ref{sec:comparison}. We present one such experiment here, deferring others to a technical report \cite{techreport}.

%Figure \ref{fig:varylocality} compares the latency for workloads with varying  geo-locality. Both \staticthree\ and \codons\ are choose replica locations randomly, and therefore their latency remains the same irrespective of the workload's geo-locality. But \auspice\ significantly improves latencies  as the geo-locality increases. Even in a workload with no locality ($g$=0.1),   \auspice\ outperforms \staticthree\ by 2$\times$ because it creates more than three replicas for each name,  and outperforms \codons\ by $4\times$  because it redirects requests to the closest replica of a name without DHT routing.

%Other experiments evaluating the sensitivity of \auspice's performance-cost trade-offs at different scales to workload parameters such as the ratio of device-to-service names, overall lookup-to-update ratio, and system parameters such as the fault-tolerance, capacity utilization, and reconfiguration epoch length are deferred to the technical report \cite{techreport}.

\rmCR{
\subsection{Simulation-based sensitivity analysis}
\label{sec:sensitivity}

In order to assess the sensitivity of \auspice's performance and cost to a wider range of system parameters, workload parameters in $\S$\ref{sec:comparison}, and scales, we use a custom simulator that simulates round-trip delays, loss, and server load-vs-response time behavior as in the PlanetLab experimental setup. We have verified \cite{techreport} that the median latencies for all simulated schemes are within 8\% of those in the emulation in $\S$\ref{sec:comparison}.   Experiments here use 10K name servers, 2K local name servers, 10K service names, and 100K device names.

%We analyze the sensitivity of \auspice's benefits to the workload parameters used in $\S$\ref{sec:comparison}. In order to be able to explore a wider range of parameters and scales, we use a custom simulator that simulates round-trip latency, loss, and server load-vs-response time behavior as measured on PlanetLab. We have verified \cite{techreport} that the median latencies for all schemes in the simulator are within 8\% of that on PlanetLab for the experiment in $\S$\ref{sec:comparison}.   Experiments here use 10K nameservers, 2K local nameservers, 10K service names, and 100K device names.

\textbf{Geo-locality.}  Figure \ref{fig:varylocality} compares the latency for workloads with varying levels of geo-locality.
Both \staticthree\ and \codons\ are choose replica locations randomly, and therefore their latency remains the same irrespective of the workload's geo-locality. But \auspice\ significantly improves latencies  as the geo-locality increases. Even in a workload with no locality ($g$=0.1),   \auspice\ outperforms \staticthree\ by 2$\times$ because it creates more than three replicas for each name,  and outperforms \codons\ by $4\times$  because it redirects requests to the closest replica of a name without the overhead of DHT routing.

\textbf{Ratio of device-to-service names.} We also evaluate schemes for workloads with different ratios of device names to service names. We fix the number of service names to be 10K and vary the number of device names between 1000 to 1M.
%\replicateall\  saturates server capacity for a workload with  DS-ratio = 1 due to high update costs. 
For the given capacity, \auspice\  can accommodate a workload with up 1M device names (while \replicateall\ can support at most 1K device names) and provides up to 6.9$\times$ lower latencies over \staticthree\  across for all ratios of service-to-device names.

@@

\textbf{Lookup-to-update ratio.} We vary the ratio of lookups to updates, termed as \emph{RW-ratio}, by increasing the number of lookups but keeping the number of updates fixed. \auspice\ provides up to 2.95$\times$ lower latencies than \codons\ and \staticthree\ for both write-dominated workload (RW-ratio $<$ 1) as well as read-dominated workloads (RW-ratio  $>$ 1). As RW-ratios increase beyond 1,  \auspice\ handles the increase in number of lookups  by automatically decreasing the replication parameter $\beta$ (refer to Eq. \ref{eq:mu}).

\blue{
\textbf{System parameters.} We also experiment with the system parameters in $\S$\ref{sec:design}, the fault tolerance threshold $F$, the capacity utilization $\mu$, and the randomness knob $\nu$. As expected, we find that as $F$ increases and approaches the total number of name servers, the cost and performance behavior increasingly mimics \static{F} until it is identical to \replicateall. Decreasing $\mu$ to small values makes \auspice's replication less aggressive hurting performance but reducing cost, while increasing $\mu$ much closer to 1 hurts latencies by overloading the system. The technical report \cite{techreport} describes these results as well as a slightly modified replica placement strategy that makes the random perturbation knob $\nu$ unnecessary (currently manually set to 0.5 in our experiments).
}
}

@@

\eat{
\begin{figure}
\centering
\includegraphics[scale=0.5]{graph/medianlatencyVSnummobile.pdf}
\vspace{-0.1in}
\caption{[Simulator] \auspice\ gives greater latency gains over \staticthree\ as the number of device names increases in  the workload.}
\label{fig:varymobile}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[scale=0.5]{graph/medianlatencyVSnummobile.pdf}
\vspace{-0.1in}
\caption{[Simulator] \auspice\ gives greater latency gains over \staticthree\ as the number of device names increases in  the workload.}
\label{fig:varymobile}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[scale=0.5]{graph/medianlatencyVSnumns.pdf}
\vspace{-0.1in}
\caption{[Simulator] \auspice\ scales well to increasing number of name servers. }
\label{fig:scalability}
\vspace{-0.1in}
\end{figure}

@@

%We summarize a few other simulation-based results here with details deferred to a techreport \cite{techreport}.

@@

%optimization formulation described in the techreport \cite{techreport}. \optimal\ decides both  replica placement and request redirection to minimize the sum of  network and server latency. The inputs  are  %We evaluate this scheme only in simulation, as it is not implemented in the prototype.

\eat{
\textbf{Optimal:} We have compared \auspice\ to \optimal\ based on an optimization formulation of the placement problem \cite{techreport}. 
\optimal\ takes as input  the set of names, their request geo-distribution, the capacity of name servers, network latency between local name servers and name servers, and a load-vs-response-time curve at each name server, and computes replica placement so as to minimize the sum of  network and server latency.
%In Figure \ref{fig:optimal}, we present the ratio of latency of \auspice\ to \optimal\  from this experiment. 
For a similar workload as in Section \ref{sec:lookup},  we find that the latency for \auspice\ is between 1.1$\times$-2.1$\times$ of the \optimal\  across all load levels. \optimal\  performs better as it can globally optimize server resource allocation across all names, but \auspice\ uses a decentralized placement algorithm to independently decide replica placement for each name. 
In ongoing work, we are evaluating \optimal\  using the testbed; this is nontrivial partly because \optimal\ must know the exact load-vs-response time behavior, which is not always stationary or easy to measure, so we conjecture that the clean simulator environment overestimates the benefits of \optimal.
}

@@

%\textbf{TTL-value selection:} \auspice\ internally uses active replication, but does allow TTL-based caching at local name servers and clients. What TTL should names use? TTL-based caching means that \verb+connect(name,port)+ calls from end-hosts can occasionally time out because the destination \verb+name+ has moved. In this case, end-hosts must send a refresh query to \auspice\ and attempt to reconnect. The overall time-to-connect to a name depends on the name's update rate, lookup rate, and the TTL. We have developed a simple analytical model to calculate the optimal TTL based on these three values \cite{techreport} to serve as a recommendation to name owners\tbd{Do we have the expression? Without an expression, this seems content-free.}.

>>>>

\subsection{\auspice\ vs. managed DNS providers}
\label{sec:managed}

%In DNS terminology, an \auspice\ name server provides the functionality of an authoritative name server -- it keeps the most up to date  name-to-address mapping of a host.

Having analyzed a synthetic workload dominated by mobile device names, we next evaluate how \auspice\ compares to commercial managed DNS providers in serving their customers' (mostly static) domain names.  These providers such as UltraDNS, DynDNS, and DNSMadeEasy \cite{ultradns, dyndns, dnsmadeeasy} offer a geo-replicated authoritative DNS service and are widely used by enterprises today (e.g., DynDNS provides DNS service for Twitter).

@@

\textbf{Lookup latency:}  
We compare \auspice\ to UltraDNS for a workload of lookup requests for  domain names serviced by the provider. 
%This experiment compares lookup latencies for \auspice\ and a leading managed DNS provider. 
%Our workload consists of lookups for  domain names serviced by the provider.  
We identify 316 domain names among top-10K Alexa websites \cite{alexa} serviced by this provider. 
The geo-distribution of lookups for each name is determined from the Alexa dataset \cite{alexa}.
For each name, we measure performance for 1000 lookups across 100 PlanetLab nodes. 
We ensure that lookups are served from the name servers maintained by the provider by requesting the address for a new random sub-domain name each time, e.g,, xyz.google.com instead of google.com. 
This name is unlikely to be cached and requires an authoritative name server lookup.
\auspice\ name servers are deployed on 80 PlanetLab locations while the managed DNS has 16 known locations of server deployments \cite{dnscompare}.  
For an even comparison between \auspice\ and the provider, we limit the maximum number of replicas/name for \auspice\ to 5, which is less than one-third the number of locations of the provider \cite{dnscompare}.  
%The geo-distribution of lookups for each domain name is determined based on the Alexa dataset \cite{alexa}.

@@

%This technique has also been used by another study \cite{dnscompare} to measure latencies to authoritative name servers.

\begin{table}[h]
\centering
\small{
\begin{tabular}{l c  c }
  & \textbf{\auspice}  & \textbf{UltraDNS}  \\ \hline
Number of replicas & 5 & 16  \\ \hline
Median Lookup Latency & 45 & 40 \\ \hline
Mean Lookup Latency & 74 & 72\\ \hline
\end{tabular}
}
\caption{\auspice\ has latencies comparable to a managed DNS provider with less than one-third replica locations.}
\label{tab:manageddns}
\end{table}

%\begin{table}[h]
%\centering
%\small{
%\begin{tabular}{l c  c  c}
%{\bf Lookup latency (ms)  $\rightarrow$} & {\bf Median}  & \textbf{Mean} & {\bf 95-\%ile}  \\ \hline
%\auspice\ &	45  & 74 & 246 \\ \hline
%Managed DNS	 & 40   & 72 & 259 \\ \hline
%\end{tabular}
%}
%\caption{\auspice\ has latencies comparable  to a managed DNS provider with less than one-third replica locations.}
%\vspace{-0.1in}
%\label{tab:manageddns}
%\end{table}

%Figure \ref{fig:manageddns} shows the CDF of the median lookup latencies across names for \auspice\ and for the managed DNS provider. The median value of the distribution in Figure \ref{fig:manageddns} is 45 ms for  \auspice\ and 40 ms for the managed DNS provider. 
Table \ref{tab:manageddns} shows median lookup latencies across names for \auspice\ and for the managed DNS provider.
\auspice\ performs within 11\% of the managed DNS provider for all latency metrics. 
While \auspice\ creates less than one-third replicas as the managed DNS provider, it places them considering the geo-distribution of demand. 
Due to its placement strategy, \auspice\ achieves  similar latency with smaller cost of updates.
% \auspice\ has a comparable latency to the managed DNS provider even with less than one-third the number of replicas for every name record as the managed DNS provider.  
%Due to a locality-aware placement,
 This experiment shows that \auspice\ provides  latencies comparable to the state-of-the-art DNS solutions with much smaller update costs due to a judicious choice of replica locations.

%This experiment shows that due to the to the geo-locality of requests for today's domain  names, a locality-aware placement reduces update costs.

\textbf{Update propagation latency:} To measure update propagation latencies, we purchase DNS service from three providers for separate domain names.  All providers replicate a name at 5 locations across US and Europe for the services we purchased. We issue address updates for the domain name serviced by that provider and then immediately start lookups to the authoritative name servers for our domain name.
These authoritative name servers can be queried only via an anycast IP address, i.e., servers at different locations advertise the same externally visible IP address. Therefore, to maximize the number of provider locations queried, we send queries from 50 random PlanetLab nodes. From each location, we periodically send queries until all authoritative name server replicas return the updated address.  The update propagation latency at a node is the time between when the node starts sending lookup to when it receives the updated address. The latency of an update is the the maximum update latency measured at any of the nodes. We measure latency of 100 updates for each provider.
 %is time difference between when we update an address and when the node gets the updated address.

To measure update latencies for \auspice, we replicate 1000 names at a fixed number of PlanetLab nodes across US and Europe. The number of nodes is chosen to be 5, 10, and 20 across three experiments. A client sends an update to the nearest node and waits for update confirmation messages from all replicas. The latency of an update is the time difference between when the client sent an update and when it received the update confirmation message from all replicas (an upper bound on the update propagation latency).  We show the distribution of measured update latencies for \auspice\ and for three managed DNS providers in Figure \ref{fig:manageddnsupdate}.

%The update latency for \auspice\ is shown based on the experiment in Section \ref{sec:lowload};  we select names replicated at 5 locations or more, because

%We issue address updates for the domain name serviced by that provider, and simultaneously start lookups to the provider's name servers from 50 PlanetLab nodes until the updated address is returned by all the name servers. 
%We issue address updates  for DNSMadeEasy using a REST-based API and for UltraDNS using a web portal.

%\begin{table}[h]
%\centering
%\small{
%\begin{tabular}{p{1.5cm}p{1cm}p{1cm}p{1cm}p{1cm}}
%{\bf Update latency(s)} & {\auspice}  & Managed DNS 1 & Managed DNS 2  & Managed DNS 3 \\ \hline
%\textbf{Median} &	0.3 & 1.4 & 1.5 & 25.0 \\ \hline
%\textbf{95-\%ile}	& 0.6 & 5.3   & 3.0 & 99.0 \\ \hline
%\end{tabular}
%}
%\caption{\auspice' update latencies are smaller than managed DNS providers for equal or more replica locations.}
%\vspace{-0.1in}
%\label{tab:manageddnsupdate}
%\end{table}

%
%\begin{figure}
%\centering
%\includegraphics[scale=0.55]{auspice/graph/newgraphs/managed-update.pdf}
%\vspace{-0.1in}
%\caption{Median  update latency of \auspice\ for updating replicas at 5 locations is  1.0 sec to 24.7 sec lower than three managed DNS providers. Values shown are 5, 25, 50, 75,  and 95 percentiles.}
%\vspace{-0.2in}
%\label{fig:manageddnsupdate}
%\end{figure}

\auspice\ provide lower update propagation latencies than all three providers for an equal or greater number of replica locations for names.  It is not clear to us why UltraDNS's update latencies are an order of magnitude higher than global propagation delays\footnote{They tend to not be forthcoming with proprietary internal details.}. This finding is consistent with a recent study \cite{dnscompare} that has shown latencies of up to tens of seconds for these providers.

%\vspace{-0.15in}
\eat{
\subsection{[Simulation]  Sensitivity analysis}
\label{sec:sensitivity}

We analyze the sensitivity of \auspice's benefits to the workload parameters used in $\S$\ref{sec:comparison}. In order to be able to explore a wider range of parameters and scales, we use a custom simulator that simulates round-trip latency, loss, and server load-vs-response time behavior as measured on PlanetLab. We have verified \cite{techreportAuspice} that the median latencies for all schemes in the simulator are within 8\% of that on PlanetLab for the experiment in $\S$\ref{sec:comparison}.   Experiments here use 10K nameservers, 2K local nameservers, 10K service names, and 100K device names.

%\auspice\ consistently gives lower lookup latencies, and its performance is robust to variations in these workload parameters.

%We present sensitivity analysis of parameters in our synthetic workload for device names: geo-locality, ratio of lookups to updates, and the distribution of lookup rates of names.  Overall, we find that our prior results are robust to variation in values of these parameters. 
%Our results show that \auspice\ consistently provides better performance for a broad range of these workload parameters.

%TBD: What is the ratio of lookups to updates for device names? What is the ratio of lookups for device names to lookups for service names?

%\begin{figure*}[ht]
%\subfigure[Geo-locality]{\label{fig:varylocality}\includegraphics[scale=0.4]{graph/medianlatencyVSlocality.pdf}}
%\subfigure[Lookup rate distribution]{\label{fig:lookupdis}\includegraphics[scale=0.4]{graph/newgraphs/lookupdis.pdf}}
%\subfigure[Ratio of device names to service names]{\label{fig:varymobile}\includegraphics[scale=0.4]{graph/medianlatencyVSnummobile.pdf}}
%\subfigure[Lookup-to-update ratio]{\label{fig:readwriteratio}\includegraphics[scale=0.4]{graph/readwriteratio.pdf}}
%\subfigure[Update cost]{\label{fig:updatebw}\includegraphics[scale=0.55]{graph/newgraphs/cdf-update-cost.pdf}}
%\vspace{-0.15in}
%\caption{[Simulator] Workload sensitivity. (a) \auspice\ gives 2$\times$ to 5$\times$  lower latencies across all locality levels. (b)  \auspice\ gives greater latency gains over \staticthree\ as the number of device names increases in  the workload.  (c) \auspice\ has lower latencies for both lookup- and update- dominated workloads. \replicateall\ is unsustainable due to high update costs and is not shown.}
%\vspace{-0.15in}
%\label{fig:lookupupdate}
%\end{figure*}

%
%\begin{figure}[t]
%\includegraphics[scale=0.5]{graph/medianlatencyVSlocality.pdf}
%\vspace{-0.1in}
%\caption{[Simulator] Workload sensitivity. \auspice\ gives 2$\times$ to 5$\times$  lower latencies across all locality levels.}
%\label{fig:varylocality}
%\vspace{-0.1in}
%\end{figure}

%  For a read-dominated workload (RW-ratio = 10), \auspice\ has 2.95$\times$ lower latency than \staticthree.

%
%\begin{figure}
%\centering
%
%\vspace{-0.1in}
%\caption{[Simulator] \auspice\ outperforms other schemes by 2$\times$ to 5$\times$  across all locality levels. \replicateall\ has  100\% request failure rate  (not shown).}
%\label{fig:varylocality}
%\vspace{-0.1in}
%\end{figure}
%
%
%\begin{figure}
%\centering
%\includegraphics[scale=0.4]{graph/newgraphs/lookupdis.pdf}
%\vspace{-0.1in}
%\caption{[Simulator] Distribution of lookup rates.}
%\label{fig:lookupdis}
%\vspace{-0.1in}
%\end{figure}
%
%
%\begin{figure}
%\centering
%\includegraphics[scale=0.5]{graph/readwriteratio.pdf}
%\vspace{-0.1in}
%\caption{[Simulator] Ratio of lookups to updates for device names. For a lookup-dominated workload (RW-ratio = 10), \auspice\ has 2.95$\times$ lower latency than \staticthree.  \replicateall\ has 100\% request failure rate (not shown).}
%\label{fig:readwriteratio}
%\vspace{-0.1in}
%\end{figure}

\textbf{Geo-locality:}  Figure \ref{fig:varylocality} compares the latency for workloads with varying levels of geo-locality.
Both \staticthree\ and \codons\ are choose replica locations randomly, and therefore their latency remains the same irrespective of workload locality. But \auspice\ can achieve better latencies  as the geo-locality in the workload increases. Even in a workload with no locality ($g=0.1$),   \auspice\ outperforms \staticthree\ by 2$\times$ because it creates more than three replicas for each name,  and outperforms \codons\ by $4\times$  because it redirects requests to the closest replica of a name unlike \codons.

\textbf{Ratio of device names to service names:} We also evaluate schemes for workloads with different ratios of device names to service names.
We fix the number of service names to be 10K and vary the number of device names between 1000 to 1,000,000.
%\replicateall\  saturates server capacity for a workload with  DS-ratio = 1 due to high update costs. 
\auspice\  can accommodate workload with up 1M device names (\replicateall\ can support at most 1K device names) and provides up to 6.9$\times$ lower latencies over \staticthree\  across for all ratios of service to device names.

@@

\textbf{Lookup-to-update ratio:} We vary the ratio of lookups to updates, termed as \emph{RW-ratio}, by increasing the number of lookups but keeping the number of updates fixed. \auspice\ provides up to 2.95$\times$ lower latencies than \codons\ and \staticthree\ for both write-dominated workload (RW-ratio $<$ 1) as well as read-dominated workloads (RW-ratios  $>$ 1). As RW-ratios increase beyond 1,  \auspice\ handles the increase in number of lookups  by decreasing the replication parameter $\beta$ (refer to Eq. \ref{eq:mu}).
}
\subsection{Scalability}
\label{sec:scalability}

\begin{figure}[t]
\centering
\includegraphics[scale=0.6]{auspice/graph/newgraphs/scalability.pdf}
\caption{\auspice's consistently gives close to 2$\times$ lower latencies for workloads with 100K-100M names.}
\vspace{-0.2in}
\label{fig:scalability}
\end{figure}

%How will \auspice\ perform at a scale of 10 billion mobile devices? 
To evaluate \auspice's key design traits at very high scales, we evaluate \auspice\ on workloads with 100K-100M device names.  We use a testbed of 200 Amazon EC2 instances, 100 each for nameservers and local nameservers respectively. We emulate wide-area latencies among servers as in the experiments in Section \ref{sec:lookup}. The experiment with a workload of 100M names included 1 billion requests with an equal number of lookups and updates sent over a 4 hour duration. Experiments with lesser number of names proportionally scale down the number of requests and the  duration.  
%As our focus is on evaluating the performance of \auspice's data plane, \auspice\ pre-computes the placement at the start of the experiment based on prior knowledge of the workload. Local name servers are also aware of the precomputed placement and they send requests directly to the active replicas in this experiment. Evaluating  \auspice's control plane performance at larger scales is part of our ongoing work.

Figure \ref{fig:scalability} shows that median lookup latency for Auspice and for \staticthree. We find that \auspice\ consistently gives close to 2$\times$ lower latency than \staticthree\ across all four workloads. 
\auspice's performance is consistent across workloads because its placement strategy ensures a similar distribution of load across name servers independent of the number of names in the workload.
Given that \auspice\ shows similar relative performance across 4 orders of magnitude of variation in the number of names, we expect these properties to persist at higher scales. Intuitively, this result is not surprising: the core of \auspice's replica placement engine is designed to make between M (the minimum required for fault-tolerance) and N (the total number of nameservers) replicas and use all available resources for intelligent replication. Group changes, although nontrivial in design, do not impose a high control overhead.

@@

\eat{
\begin{figure}
\centering
\includegraphics[scale=0.5]{auspice/graph/medianlatencyVSnummobile.pdf}
\vspace{-0.1in}
\caption{[Simulator] \auspice\ gives greater latency gains over \staticthree\ as the number of device names increases in  the workload.}
\label{fig:varymobile}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[scale=0.5]{auspice/graph/medianlatencyVSnummobile.pdf}
\vspace{-0.1in}
\caption{[Simulator] \auspice\ gives greater latency gains over \staticthree\ as the number of device names increases in  the workload.}
\label{fig:varymobile}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[scale=0.5]{auspice/graph/medianlatencyVSnumns.pdf}
\vspace{-0.1in}
\caption{[Simulator] \auspice\ scales well to increasing number of name servers. }
\label{fig:scalability}
\vspace{-0.1in}
\end{figure}

@@

%We summarize a few other simulation-based results here with details deferred to a techreport \cite{techreportAuspice}.

@@

%optimization formulation described in the techreport \cite{techreportAuspice}. \optimal\ decides both  replica placement and request redirection to minimize the sum of  network and server latency. The inputs  are  %We evaluate this scheme only in simulation, as it is not implemented in the prototype.

\eat{
\textbf{Optimal:} We have compared \auspice\ to \optimal\ based on an optimization formulation of the placement problem \cite{techreportAuspice}. 
\optimal\ takes as input  the set of names, their request geo-distribution, the capacity of name servers, network latency between local name servers and name servers, and a load-vs-response-time curve at each name server, and computes replica placement so as to minimize the sum of  network and server latency.
%In Figure \ref{fig:optimal}, we present the ratio of latency of \auspice\ to \optimal\  from this experiment. 
For a similar workload as in Section \ref{sec:lookup},  we find that the latency for \auspice\ is between 1.1$\times$-2.1$\times$ of the \optimal\  across all load levels. \optimal\  performs better as it can globally optimize server resource allocation across all names, but \auspice\ uses a decentralized placement algorithm to independently decide replica placement for each name. 
In ongoing work, we are evaluating \optimal\  using the testbed; this is nontrivial partly because \optimal\ must know the exact load-vs-response time behavior, which is not always stationary or easy to measure, so we conjecture that the clean simulator environment overestimates the benefits of \optimal.
}

@@

%\textbf{TTL-value selection:} \auspice\ internally uses active replication, but does allow TTL-based caching at local name servers and clients. What TTL should names use? TTL-based caching means that \verb+connect(name,port)+ calls from end-hosts can occasionally time out because the destination \verb+name+ has moved. In this case, end-hosts must send a refresh query to \auspice\ and attempt to reconnect. The overall time-to-connect to a name depends on the name's update rate, lookup rate, and the TTL. We have developed a simple analytical model to calculate the optimal TTL based on these three values \cite{techreportAuspice} to serve as a recommendation to name owners\tbd{Do we have the expression? Without an expression, this seems content-free.}.

### 2015-06-10 auspice_prev/implementation.tex
Initial import of thesis starting from proposal document
Includes all files: tex, pdf, etc.

\eat{
\subsection{Instantiating a global name service}
\label{sec:impl}

@@

%\vsp
\subsubsection{Implementation status}

%\begin{table}[t]
%\centering
%\small{
%\begin{tabular}{c|c}
%{\bf \auspice\ parameter} & {\bf Value}\\ \hline
%Min number of replicas ($M$) & 3 \\ \hline
%Number of replicas placed \\according to locality ($K$) & 5 \\ \hline
%\end{tabular}
%}
%\caption{Parameters for \auspice.}
%\vspace{-0.3in}
%\label{tab:auspiceparam}
%\end{table}

@@

We have implemented \auspice\ as described in Java with 28K lines of code. We have been maintaining an alpha deployment for research use for many months across eight EC2 regions. We have implemented support for two pluggable NoSQL data stores, MongoDB (default) and Cassandra, as persistent local stores at servers. We do not rely on any distributed deployment features therein as the coordination middleware is what \auspice\ provides.

%Even for eventual consistency, each name needs at least one Paxos instance maintained by each of its replica-controllers to perform group changes correctly, which would nominally result in an average of $MN/S$ instances per name server (where N is the total number of names; S and M are respectively the total and minimum number of replicas required for fault-tolerance). To reduce the number of Paxos instances for eventual consistency, we have integrated consistent hashing with a combined Paxos implementation that maintains just $M$ instances per name server. The set of replica-controllers for a name computed using consistent hashing is the same for roughly N/S names, so a single Paxos instance can be used for all of these names. Group change operations across these N/S (otherwise unrelated) names must be committed sequentially but can be issued in parallel.

@@

>>>>

%!TEX root = Main.tex
\eat{
\subsection{Instantiating a global name service}
\label{sec:impl}

@@

%\vsp
\subsubsection{Implementation}
\vsp
%\begin{table}[t]
%\centering
%\small{
%\begin{tabular}{c|c}
%{\bf \auspice\ parameter} & {\bf Value}\\ \hline
%Min number of replicas ($M$) & 3 \\ \hline
%Number of replicas placed \\according to locality ($K$) & 5 \\ \hline
%\end{tabular}
%}
%\caption{Parameters for \auspice.}
%\vspace{-0.3in}
%\label{tab:auspiceparam}
%\end{table}

@@

The core of \auspice\ is implemented in Java with 28K lines of code. We have been running an alpha deployment for research use for several months across eight EC2 regions with support for an HTTP interface \cite{gnrswebsite}. We have implemented support in \auspice\ for two pluggable NoSQL data stores, MongoDB (default) and Cassandra, as persistent local stores at name servers. We do not rely on any distributed deployment features therein as the coordination middleware is our  contribution.

Even for eventual consistency, each name needs at least one Paxos instance maintained by each of its replica-controllers to perform group changes correctly, which would nominally result in an average of $MN/S$ instances per name server (where N is the total number of names; S and M are respectively the total and minimum number of replicas required for fault-tolerance). To reduce the number of Paxos instances for eventual consistency, we have integrated consistent hashing with a combined Paxos implementation that maintains just $M$ instances per name server. The set of replica-controllers for a name computed using consistent hashing is the same for roughly N/S names, so a single Paxos instance can be used for all of these names. Group change operations across these N/S (otherwise unrelated) names must be committed sequentially but can be issued in parallel.

@@

We have developed a simple NCS as a proof-of-concept, which through a web portal (\verb+http://gns.name+) or a command-line console allows a user to bind a self-  or system-selected GUID to a human-readable name that is simply an email address, i.e., our proof-of-concept NCS is a trivial CA that relies on email-based identity verification. Clients currently have to use a custom Auspice developer library to perform lookups and updates. We are in the process of developing a proxy to translate between BIND and \auspice's wireline protocol to interoperate with DNS.
